---
title: "Extensive EDA - Kaggle Survey 2018"
author: "Bhavani"
date: "June 19, 2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

Loading Libraries
```{r}
library(readr)
library(purrr)
library(dplyr)
library(ggplot2)
library(stringr)

```

Load the data 
```{r}


survey1 <- read_csv("C:Users/BhavaniC/Downloads/multipleChoiceResponses.csv")
survey2 <- read_csv("C:Users/BhavaniC/Downloads/freeFormResponses.csv")
```

Let's look at the Gender of the Respondents.

```{r}
gender <- survey1 %>% filter(Q1 == "Male"| Q1 == "Female") %>% group_by(Q1) %>% summarise(count = n())

ggplot(data=gender, aes(x = Q1 , y = count/sum(count))) + geom_bar(stat = "identity") + xlab("Gender") +ylab("Respondents") + scale_y_continuous(labels = scales::percent)
```

We can see from the plot above, that more than 80% of the respondents were Men. It would also be interesting to see the respondents' home countries.

```{r}
countries <- survey1  %>% group_by(Q3)  %>% summarise(count = n()) %>% arrange(desc(count)) %>% top_n(10)
  
  
ggplot(data=countries, aes(x = reorder(Q3,count) , y = count/sum(count))) + geom_bar(stat = "identity") + xlab("Gender") +ylab("Respondents")  + coord_flip() + scale_y_continuous( labels = scales::percent) 
```

Most kaggle users seem to be from USA or India. These two countries are dominant. 

Let's also check their academic backgrounds. Are people looking to study Data Science after obtaining a graduate degree ?



```{r}
survey1 %>% filter(Q1 == "Female" | Q1 == "Male") %>% ggplot(aes(Q4)) +geom_bar(aes(fill = Q1)) + theme(axis.text.x = element_text(angle = 15,hjust = 0.5, size =7)) +theme(legend.position="none")+xlab("Academic qualification ")+
scale_x_discrete(labels = function(x) str_wrap(x, width = 8))
```
Most Kaggle users seem to have either a Bachelor's Degree or a Master's Degree. It seems that people with an advanced degree are interested in  pursuing a career in data science. 

Let's try to understand how old the users are.

```{r}
survey1 %>% filter(Q1 == "Female" | Q1 == "Male")  %>% ggplot(aes(Q2)) + geom_bar(aes(fill = Q4)) +xlab("Age Group") + coord_flip() 
```

Kaggle is used by people in the 25-29 age group , followed closely by people in the 22-24 age group. Most of these users have a Master's degree.



