#Exploratory Analysis

##Loading Packages
```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(purrr)

forestfires <- read_csv("//dc1/Folder Redirection/BhavaniC/Documents/GitHub/DataScienceProjects/Visualizing Forest Fire Data/forestfires.csv")
```

During which months are forest fires most common ? Which day of the week do they tend to occur ?

```{r}
d1 <- forestfires %>% group_by(month) %>% summarise(count = n())
d1 <- d1 %>% mutate(month = factor(month, levels = c("jan","feb","mar","apr","may","jun","jul","aug","sep","oct","nov","dec")))
ggplot(data = d1, aes(x= month, y = count)) + geom_bar(stat = "identity")
```

Maximum number of fires occur in August and September.The least number of fires occur in November. 

```{r}
d2 <- forestfires %>% group_by(day) %>% summarise(count = n())
d2 <- d2 %>% mutate(day = factor(day,levels = c("sun","mon","tue","wed","thu","fri","sat")))
ggplot(data = d2, aes(x= day, y = count)) + geom_bar(stat = "identity")

```

Largest number of forestfires have occured on a Sunday.The least number of fires occur on Wednesdays.

Lets visualize the distribution of the features by month and week.


```{r}
create_boxplot1 <- function(x,y)
{
  ggplot(data = forestfires, aes_string(x = x, y=y)) + geom_boxplot(alpha = 0.3) + theme(panel.background = element_rect(fill = "white"))
}
y_var <- names(forestfires)[5:13]
x_var <- names(forestfires)[3]
map2(x_var,y_var,create_boxplot1)
```

```{r}
create_boxplot2 <- function(x,y)
{
  ggplot(data = forestfires, aes_string(x = x, y=y)) + geom_boxplot(alpha = 0.3) + theme(panel.background = element_rect(fill = "white"))
}
y_var <- names(forestfires)[5:13]
x_var <- names(forestfires)[4]
map2(x_var,y_var,create_boxplot2)
```

Certain features like temp and Drought Code seem to be correlated to the high number of forest fires. We can look at a scatter plot of these variables to establish a correlation (if any)

```{r}
create_scatterplt <- function(x,y)
{
  ggplot(data = forestfires, aes_string(x = x, y=y)) + geom_point(alpha = 0.3) + theme(panel.background = element_rect(fill = "white")) 
}
x_var <- names(forestfires)[5:12]
y_var <- names(forestfires)[13]
map2(x_var,y_var,create_scatterplt)
```

Those plots did not tell a clear story. Let us look at a histogram of area.

```{r}
ggplot(data=forestfires,aes(x=area)) + geom_histogram(bins = 30)
```

A large number of observations are 0.Lets filter out these values and then create scatter plots to extract more meaning.

```{r}
rem_zeroes <- forestfires %>% filter(area!=0)
create_scatterplt <- function(x,y)
{
  ggplot(data = rem_zeroes, aes_string(x = x, y=y)) + geom_point(alpha = 0.3) + theme(panel.background = element_rect(fill = "white")) + ylim(1,10)
}
x_var <- names(forestfires)[5:12]
y_var <- names(forestfires)[13]
map2(x_var,y_var,create_scatterplt)
```

It appears that there is no correlation between area and the other features. 